---
title: "WRIA_Api_Data_Pull"
output: html_document
---


```{r setup, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
startTime <- Sys.time()

libs <- readLines("Data/Libraries.txt")
sapply(libs, require, character.only=TRUE)

source("WRIA_Api_Data_Source.R")

#read in and validate user input, convert char to logical where possible
userInput <- readReportRequest()
#Tidy up refuge name
dataName <- gsub(" ", "", str_to_title(userInput$Refuge))


#Get refuge data and relevant NWIS and WQP data for either approved or interest boundaries
if(userInput$Approved){
  fwsRefuge <- getFWSCadastral(userInput$Refuge,approved=TRUE) 
  refugeData <- createSiteObject(fwsRefuge, userInput$NWIS, userInput$WQP, buffer=TRUE)
  #write data to specified output folder
  writeFWSCadastral(fwsRefuge,sprintf("%sApproved_ShapeFile",dataName),userInput$ResultFolder)
  write.csv(refugeData@availableWqpData,sprintf("%s/%s_fwsAppAvailableWqpData.csv",
                                                userInput$ResultFolder,dataName))
  write.csv(refugeData@availableNwisData,sprintf("%s/%s_fwsAppAvailableNwisData.csv",
                                                 userInput$ResultFolder,dataName))
}else{
  fwsRefuge <- getFWSCadastral(userInput$Refuge)
  refugeData <- createSiteObject(fwsRefuge, userInput$NWIS, userInput$WQP, buffer=TRUE)
  writeFWSCadastral(fwsRefuge,sprintf("%s_interest",dataName),userInput$ResultFolder)
  write.csv(refugeData@availableWqpData,sprintf("%s/%s_fwsIntAvailableWqpData.csv",
                                                userInput$ResultFolder,dataName))
  write.csv(refugeData@availableNwisData,sprintf("%s/%s_fwsIntAvailableNwisData.csv",
                                                 userInput$ResultFolder,dataName))
}

#Get intersecting huc8 data and relavant NWIS and WQP data
if(userInput$HUC8){
  huc8 <- getHucs("WBDHU8",fwsRefuge)
  huc8Data <- createSiteObject(huc8,userInput$NWIS,userInput$WQP)
  #write data to specified output folder
  write.csv(huc8Data@availableWqpData,sprintf("%s/%s_huc8AvailableWqpData.csv",
                                                userInput$ResultFolder,dataName))
  write.csv(huc8Data@availableNwisData,sprintf("%s/%s_huc8AvailableNwisData.csv",
                                                 userInput$ResultFolder,dataName))
}else{
  huc8 <- NULL
  huc8Data <- NULL
}

#Get intersecting huc10 data and relavant NWIS and WQP data
if(userInput$HUC10){
  huc10 <- getHucs("WBDHU10",fwsRefuge)
  huc10Data <- createSiteObject(huc10,userInput$NWIS,userInput$WQP)
  #write data to specified output folder
  write.csv(huc10Data@availableWqpData,sprintf("%s/%s_huc10AvailableWqpData.csv",
                                                userInput$ResultFolder,dataName))
  write.csv(huc10Data@availableNwisData,sprintf("%s/%s_huc10AvailableNwisData.csv",
                                                 userInput$ResultFolder,dataName))
}else{
  huc10 <- NULL
  huc10Data <- NULL
}

# Get the current parameter lookup table
paramLookup <- read.xlsx("Data/paramLookup.xlsx")
paramLookup$parm_cd <- str_pad(paramLookup$parm_cd, 5, side="left", pad="0")

# get the state limits table
limLookup <- read.xlsx("Data/limitLookup.xlsx")
limLookup$PCODE <- str_pad(limLookup$PCODE, 5, side="left", pad="0")

```

## R Markdown

This report presents data downloaded on `r Sys.Date()` from the USGS and EPA hydrologic and water quality database accessed via the R dataRetrieval package (de Cicco et al. 2018).  The report runs based on user input supplied in the file: *ReportRequest.xlsx*.  Resulting data are saved into a project folder and presented for inspection in this interactive html report.  



# `r unique(fwsRefuge$ORGNAME)`

## Refuge Boundaries and Associated Hydrologic Units

The refuge intersects `r nrow(huc8)` HUC8 (`r unique(huc8$NAME)`) and `r nrow(huc10)` HUC10 (`r unique(huc10$NAME)`) units.  

```{r, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
hucPlot <- generatePlot(fwsRefuge,huc8,huc10)
hucPlot
```
